Closed-loop Neuromorphic Benchmarks

### 2015-10-01 paper/paper.tex
Added model summary

>>>>

For each of three hardware platforms, we implemented the neural control
system with the learning rule described above.  That is, we started with a
standard non-neural PD controller that produced an output $u$.  The state
information $q$ was fed into a group of neurons using randomly generated
input weights, producing output activity $A$.  The actual output to the motor
was $u+Ad$ where $d$ is a vector of learned weights, initialized to all
zeros.  The learning rule was $\Delta d=\alpha A \times u$, and the
learning rate $\alpha$ was fixed at 0.001.
